---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

```{r, echo = FALSE}
version <- as.vector(read.dcf("DESCRIPTION")[, "Version"])
version <- gsub("-", ".", version)
```

[![license](https://img.shields.io/badge/license-GPL--2-lightgrey.svg)](https://choosealicense.com/)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/toxval/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
[![DOI](https://zenodo.org/badge/760193848.svg)](https://zenodo.org/doi/10.5281/zenodo.12753573)
<!-- badges: end -->

## Overview 

`toxval` package extracts NSEC or ECx estimates from supported fitted frequentest (drc) and Bayesian (bayesnec) model objects. For more details see [Fisher & Fox (2023)](https://doi.org/10.1002/etc.5610).

## Installation

The current development version can be downloaded from GitHub via

```{r eval=FALSE}
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
remotes::install_github("open-aims/toxval", ref = "main")
```

## Usage

Usage and further information about `toxval` can be seen on the [project
page](https://open-aims.github.io/toxval/) and the
[reference page](https://open-aims.github.io/toxval/reference/).

## Further Information

`toxval` is provided by the
[Australian Institute of Marine Science](https://www.aims.gov.au) and Poisson Consulting under the
GPL-2 License ([GPL-2](https://opensource.org/license/gpl-2-0/)).
